eRFM `r customerName`
========================================================

### Sales Items data to analize
##### Files: `r fileNames`
#### Affected years (parameter rfm_calc_years), minimum and  maximum purchase dates :
```{r echo=FALSE, comment=""}
cat("rfm_calc_years parameter:",rfm_calc_years,"; Data from:",as.character(min(act_sales_item$OrderDate)), "; to:", as.character(max(act_sales_item$OrderDate)))
```
#### Make sure the Monetary values are bigger or equal then zero, and there are no NULL or bad values in Order Date
```{r echo=FALSE}
if (na_monetary.count > 0) {
  cat(paste("Count of NA Monetary values:",na_monetary.count,". There might be NA value in order file prize column. "), "\n")
  cat("CustomerID example(s):",head(as.character(na_monetary.examples)), "was (were) excluded from analisys")
}

if (negative_monetary.count > 0) {
  percent <- round(negative_monetary.count/length(unique(sales_cust$CustomerID))*100,2)
  cat(paste("Number of contacts with a negative turnover (Monetary) for the given time period:",negative_monetary.count,' (', percent, '% of the contacts)'), "\n")
  cat("CustomerID example(s):",head(as.character(negative_monetary.examples)), "was (were) excluded from analisys")
} else {
  cat(paste("Count of negative Monetary values:",negative_monetary.count))
}

if (length(order_date_na_examples) > 0) {
  cat(paste("Count of NULL or bad values in Order Date:",length(order_date_na_examples)), "\n")
  cat("OrderID example(s):",head(as.character(order_date_na_examples)), "was (were) excluded from analisys")
}

```

### Frequency
#### Frequency Table
```{r echo=FALSE, comment=""}

tFreq <- as.data.frame(table(salesRFM$Frequency))
names(tFreq)[2] <- "F"
maxFreq <- max(salesRFM$Frequency)
xlim_to <- 10
if (nrow(tFreq) > 31) {
  tFreqPart <- tFreq[1:30,]
  levels(tFreqPart$Var1) <- c(levels(tFreqPart$Var1), ">30")
  tFreqPart <- rbind(tFreqPart,c(">30",sum(tFreq[31:nrow(tFreq),]$F)))
  tFreq <- tFreqPart
  maxFreq <- as.numeric(tFreq[30,"Var1"])
  xlim_to <- 20
}
tFreq$id <- 1
kable(reshape(tFreq, direction = "wide", timevar="Var1", idvar="id"))
```
#### Frequency - 30
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
fc_breaks <- as.numeric(names(table(salesRFM$Frequency)))
fc_df <- salesRFM[,c("Frequency", "Monetary")]
show_intervals (df <- fc_df, 
                p_breaks <- fc_breaks, 
                p_title = paste("Frequency - first timers vs recurring"), 
                p_xlim = c(0,xlim_to), p_bw=0.5, p_write_ints=FALSE)

```

#### Frequency - first timers vs recurring
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}

fc_breaks <- c(1,2,max(salesRFM$Frequency))
fc_df <- salesRFM[,c("Frequency", "Monetary")]
show_intervals (df <- fc_df, 
                p_breaks <- fc_breaks, 
                p_title = paste("Frequency - first timers vs recurring"), 
                p_xlim = c(0,xlim_to), p_bw=0.5)

```

The recurring customers (`r round(dim(salesRFM[salesRFM$Frequency > 1,])[1]/dim(salesRFM[,])[1]*100,2)` % of whole population) are responsible for the `r round(sum(salesRFM[salesRFM$Frequency > 1,]$Monetary)/sum(salesRFM$Monetary)*100,2)`% of Total Revenue. The first timers are (`r round(dim(salesRFM[salesRFM$Frequency == 1,])[1]/dim(salesRFM[,])[1]*100,2)` % of whole population) are responsible for the `r round(sum(salesRFM[salesRFM$Frequency == 1,]$Monetary)/sum(salesRFM$Monetary)*100,2)`% of Total Revenue.

First timer customers average spent value: `r round(mean(salesRFM[salesRFM$Frequency == 1,]$Monetary)[1])` 
Recurring customers average spent value: `r round(mean(salesRFM[salesRFM$Frequency > 1,]$Monetary)[1])` 

### Conversion Period
#### Conversion Period - based on quantiles
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
cpq_probs <- c(0,0.50,0.95,1.0)
cpq_breaks <- quantile(salesRFM[salesRFM$Frequency > 1,c("ConversionPeriod")], probs=cpq_probs)
cpq_df <- salesRFM[salesRFM$Frequency > 1,c("ConversionPeriod", "Monetary")]
show_intervals (df <- cpq_df, 
                p_breaks <- cpq_breaks, 
                p_title = paste("Conversion Period - quantiles:",paste(cpq_probs,collapse=",")), 
                p_xlim = NULL#c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 4)
)
```

### Activity Period
#### Activity Period - based on quantiles
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
ap_probs <- c(0,0.50,0.95,1.0)
ap_breaks <- quantile(salesRFM[salesRFM$Frequency > 1,c("ActivityPeriod")], probs=ap_probs)
ap_df <- salesRFM[salesRFM$Frequency > 1,c("ActivityPeriod", "Monetary")]
show_intervals (df <- ap_df, 
                p_breaks <- ap_breaks, 
                p_title = paste("ActivityPeriod - quantiles:",paste(ap_probs,collapse=",")), 
                NULL
)
```

### Recency
#### Recurring recency - kmeans
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
display_kmeans (salesRFM[salesRFM$Frequency > 1,c("Recency", "Monetary")], 10, 20, "Recency", NULL,max(salesRFM$Recency))
```

#### Recurring recency - by quantiles
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
rq_probs <- c(0,0.50,0.95,1.0)
rq_breaks <- quantile(salesRFM[salesRFM$Frequency > 1,c("Recency")], probs=rq_probs)
rq_df <- salesRFM[salesRFM$Frequency > 1,c("Recency", "Monetary")]
show_intervals (df <- rq_df, 
                p_breaks <- rq_breaks, 
                p_title = paste("Recency - recurring, quantiles:",paste(rq_probs,collapse=",")), 
                NULL
)
```

#### Whole population recency - by custom
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
#rc_breaks <- c(0, 70, 370,731)

#get the custom breaks from conversion period quantiles
rc_breaks <- cpq_breaks
#change the last interval end to the maximum of recency from the whole population
rc_breaks[4] <- max(salesRFM$Recency)

rc_df <- salesRFM[,c("Recency", "Monetary")]
show_intervals (df <- rc_df, 
                p_breaks <- rc_breaks, 
                p_title = paste("Recency - whole population, custom: ",paste(rc_breaks,collapse=",")) , 
                p_xlim = NULL#c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 4)
)

```

#### 1st timers recency - by custom
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
#rc_breaks <- c(0, 70, 370,731)

#get the custom breaks from conversion period quantiles
rc_breaks <- cpq_breaks
#change the last interval end to the maximum of recency from the whole population
rc_breaks[4] <- max(salesRFM$Recency)

rc_fst_df <- salesRFM[salesRFM$Frequency == 1,c("Recency", "Monetary")]
show_intervals (df <- rc_fst_df, 
                p_breaks <- rc_breaks, 
                p_title = paste("Recency - 1st timers, custom: ",paste(rc_breaks,collapse=",")) , 
                p_xlim = NULL#c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 4)
)
```

#### Group counts based on custom recency intervals
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
#assign contacts into groups by custom recency intervals
salesRFM$rankRC=cut(salesRFM$Recency, breaks=rc_breaks, include.lowest=TRUE, dig.lab=10)
```
##### 1st Timers
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
#1st timers
table(salesRFM[salesRFM$Frequency == 1,]$rankRC)
```
##### Recurring
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
#recurring
table(salesRFM[salesRFM$Frequency > 1,]$rankRC)
```

### Monetary
#### Monetary - kmeans
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
exclude_top_n <- 10
if (exclude_top_n > 0) {
  print(paste("Top", exclude_top_n, "excluded customer by monetary:"))
  print(as.data.frame(break_df_by_top_nth_value(salesRFM[,c("CustomerID", "Monetary")], 2, exclude_top_n)$top))
}
display_kmeans (
  df <- salesRFM[,c("Monetary", "Monetary")], 
  p_centers <- 5, 
  p_nstart <- 20, 
  p_title <- "Monetary", 
  p_xlim <- c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 8),
  original_max_value <- -1,
  p_exclude_top_n <- exclude_top_n
  )
```

#### Monetary - by custom
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
max(salesRFM$Monetary)

#Add custom monetary limits:
mc_breaks <- c(0,800, 2625, 10120, 40765, 42394)
mc_df <- salesRFM[,c("Monetary", "Monetary")]

show_intervals (df <- mc_df, 
                p_breaks <- mc_breaks, 
                p_title = "Monetary", 
                p_xlim = c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 4)
                )
```
#### Registration date and First order distance density
```{r echo=FALSE, comment="", fig.width=10, fig.height=8}
if (exists("customer",mode="any"))
  if (!is.null(customer))
    hist(as.integer(customer$first_order_distance), col="blue", lwd=2, main="First order distance histogram", ylab="Count of contacts", xlab="Elapsed days between the registration and the first order")
```
