eRFM `r customerName`
========================================================

### Sales Items data to analize
##### Files: `r fileNames`
#### Affected years (parameter rfm_calc_years), minimum and  maximum purchase dates :
```{r echo=FALSE, comment=""}
cat("rfm_calc_years parameter:",rfm_calc_years,"; Data from:",as.character(min(act_sales_item$OrderDate)), "; to:", as.character(max(act_sales_item$OrderDate)))
```
#### Make sure the Monetary values are bigger or equal then zero, and there are no NULL or bad values in Order Date
```{r echo=FALSE}
if (na_monetary.count > 0) {
  cat(paste("Count of NA Monetary values:",na_monetary.count,". There might be NA value in order file prize column. "), "\n")
  cat("CustomerID example(s):",head(as.character(na_monetary.examples)), "was (were) excluded from analisys")
}

if (negative_monetary.count > 0) {
  percent <- round(negative_monetary.count/length(unique(sales_cust$CustomerID))*100,2)
  cat(paste("Number of contacts with a negative turnover (Monetary) for the given time period:",negative_monetary.count,' (', percent, '% of the contacts)'), "\n")
  cat("CustomerID example(s):",head(as.character(negative_monetary.examples)), "was (were) excluded from analisys")
} else {
  cat(paste("Count of negative Monetary values:",negative_monetary.count))
}

if (length(order_date_na_examples) > 0) {
  cat(paste("Count of NULL or bad values in Order Date:",length(order_date_na_examples)), "\n")
  cat("OrderID example(s):",head(as.character(order_date_na_examples)), "was (were) excluded from analisys")
}

```

### Frequency
#### Frequency - first timers vs recurring
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
tFreq <- as.data.frame(table(salesRFM$Frequency))
names(tFreq)[2] <- "F"
maxFreq <- max(salesRFM$Frequency)
xlim_to <- 10
if (nrow(tFreq) > 31) {
  xlim_to <- 20
}

fc_breaks <- c(1,2,max(salesRFM$Frequency))
fc_df <- salesRFM[,c("Frequency", "Monetary")]
show_intervals (df <- fc_df, 
                p_breaks <- fc_breaks, 
                p_title = paste("Frequency - first timers vs recurring"), 
                p_xlim = c(0,xlim_to),
                p_bw=0.5
                )

```

The recurring customers (`r round(dim(salesRFM[salesRFM$Frequency > 1,])[1]/dim(salesRFM[,])[1]*100,2)` % of whole population) are responsible for the `r round(sum(salesRFM[salesRFM$Frequency > 1,]$Monetary)/sum(salesRFM$Monetary)*100,2)`% of Total Revenue. The first timers are (`r round(dim(salesRFM[salesRFM$Frequency == 1,])[1]/dim(salesRFM[,])[1]*100,2)` % of whole population) are responsible for the `r round(sum(salesRFM[salesRFM$Frequency == 1,]$Monetary)/sum(salesRFM$Monetary)*100,2)`% of Total Revenue.

First timer customers average spent value: `r round(mean(salesRFM[salesRFM$Frequency == 1,]$Monetary)[1])` 
Recurring customers average spent value: `r round(mean(salesRFM[salesRFM$Frequency > 1,]$Monetary)[1])` 

### Activity Period
#### Activity Period - based on quantiles
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
ap_probs <- c(0,0.50,0.95,1.0)
ap_breaks <- quantile(salesRFM[salesRFM$Frequency > 1,c("ActivityPeriod")], probs=ap_probs)
ap_df <- salesRFM[salesRFM$Frequency > 1,c("ActivityPeriod", "Monetary")]
cat(paste("Count of recurring customers:",length(ap_df$ActivityPeriod)))
show_intervals (df <- ap_df, 
                p_breaks <- ap_breaks, 
                p_title = paste("ActivityPeriod - quantiles:",paste(ap_probs,collapse=",")), 
                NULL
)
```

### Recency
#### Whole population recency - by custom
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
#rc_breaks <- c(0, 70, 370,731)

#get the custom breaks from conversion period quantiles
rc_breaks <- ap_breaks
#change the last interval end to the maximum of recency from the whole population
rc_breaks[4] <- max(salesRFM$Recency)

rc_df <- salesRFM[,c("Recency", "Monetary")]
show_intervals (df <- rc_df, 
                p_breaks <- rc_breaks, 
                p_title = paste("Recency - whole population, custom: ",paste(rc_breaks,collapse=",")) , 
                p_xlim = NULL#c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 4)
)

```

### Monetary
#### Monetary - kmeans
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
exclude_top_n <- 10
cat(paste( "Top", exclude_top_n, "excluded"))
display_kmeans (
  df <- salesRFM[,c("Monetary", "Monetary")], 
  p_centers <- 5, 
  p_nstart <- 20, 
  p_title <- "Monetary", 
  p_xlim <- c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 8),
  original_max_value <- -1,
  p_exclude_top_n <- exclude_top_n
  )
```


#### Monetary - by custom
```{r echo=FALSE, comment="", fig.width=12, fig.height=10}
#cat(paste("Max. monetary value:",max(salesRFM$Monetary)))

#Add custom monetary limits:
#mc_breaks <- c(0,100, 250, 500, 1000, 42394)
#mc_df <- salesRFM[,c("Monetary", "Monetary")]

#show_intervals (df <- mc_df, 
#                p_breaks <- mc_breaks, 
#                p_title = "Monetary", 
#                p_xlim = c(0,quantile(salesRFM$Monetary, 0.75) + IQR(salesRFM$Monetary) * 4)
#                )
```